$\pi$ with leftovers: \\ a mechanisation in Agda

### 2020-09-11 paper/paper.tex
a pass on abstract

\begin{abstract}
  The \picalc{} is a computational model for communication and concurrency.
  The \emph{linear} \picalc{} is a typed version of the \picalc{} where channels must be used exactly once.
  It is an underlying theoretical and practical framework on top of which more advanced types and theories can be built, including \emph{session types} \cite{H93,THK94,HVK98}.

  We present an untyped syntax and semantics for the \picalc{}.
  We provide a resource-aware type system parametrised by a set of multiplicity algebras.
  This allows the user to mix \emph{linear}, \emph{graded} and \emph{shared} types.
  We use leftover typing \cite{Allais2018a} to encode our typing rules, thus avoiding the ubiquitous context splitting proofs so common in type systems for linear calculi.
  We provide a framing theorem, and generalise the weakening and strengthening theorems, and use them to prove subject congruence.
  We show that the type system is stable under substitution and prove subject reduction.
%
  Our formalisation is fully mechanised in Agda.
\end{abstract}

>>>>

\begin{abstract}
  The \picalc{} is a computational model for communication and concurrency.
  The \emph{linear} \picalc{} is a typed version of the \picalc{} where channels must be used exactly once.
  It is an underlying theoretical and practical framework on top of which more advanced types and theories can be built, such as \emph{session types} \cite{H93,THK94,HVK98}.

  We present an untyped syntax and semantics for the \picalc{}, on top of which we provide a resource-aware type system parametrised by a set of multiplicity algebras.
  This allows the user to mix \emph{linear}, \emph{graded} and \emph{shared} types, under the same unified framework.
  We use leftover typing \cite{Allais2018a} to encode our typing rules, thus avoiding the ubiquitous context splitting proofs, which are mandatory when dealing with linear type systems.
  We provide a framing theorem, and generalise the weakening and strengthening theorems, and use them to prove subject congruence.
  We show that the type system is stable under substitution and prove subject reduction.
%
  Our formalisation is fully mechanised in Agda.
\end{abstract}
